Efficient pedigree recording for fast population genetics simulation

### 2017-12-28 forwards_paper.tex
update bit on parallelization

Simulating very large populations and entire genomes will likely require parallelization.
The one-way nature of information flow here makes our scheme relatively easy to incorporate
into a parallel algorithm.
Recently, \citet{lawrie2017accelerating} used parallelization
to improve performance for the ``Poisson Random Field'' (PRF) family of models~\citep{Sawyer1992-jw},
in which mutations are unlinked and there is no effect of genetic background on fitness.
However, thus far little attention has been paid to parallelization of simulations involving linkage, which is much more
complex than the PRF model.

>>>>

Simulating very large populations and entire genomes will likely require parallelization.
The one-way nature of information flow here makes our scheme relatively easy to incorporate
into a parallel algorithm.
Recently, \citet{lawrie2017accelerating} used parallelization
to improve performance for the ``Poisson Random Field'' (PRF) family of models~\citep{Sawyer1992-jw},
in which mutations are unlinked and there is no effect of genetic background on fitness.
However, thus far little attention has been paid to parallelization of simulations involving linkage, as our simulations
where do, which is much more
complex than the PRF model.
